Case study validations of automatic bullet matching

### 2018-10-09 index.Rmd
Add comment color, use styler to clean up code in the file according to tidyverse style guidelines

---
\newcommand{\hh}[1]{{\textcolor{orange}{#1}}}
\noindent

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  error = FALSE, 
  collapse = TRUE,
  comment = "",
  fig.height = 6,
  fig.width = 6,
  fig.align = "center",
  out.width= '\\textwidth',
  cache = FALSE,
  fig.path='figures/',
  echo=FALSE
)
options(knitr.table.format = "latex")

@@

```{r functions}
estimateBeta <- function(x, method = "mm", probs=c(0.25, 0.75)) {
  if (method =="mm") {
    mu = mean(x, na.rm=TRUE)
    sd = sd(x, na.rm=TRUE)
    lambda <- mu/sd*(1-mu)/sd - 1
    alpha <- mu*lambda
    beta <- (1-mu)*lambda
  }
  if (method =="LB") {
    quantile1=list(p=probs[1],x=quantile(probs=probs[1], x))
    quantile2=list(p=probs[2],x=quantile(probs=probs[2], x))
    bs <- LearnBayes::beta.select(quantile1,quantile2)
    alpha = bs[1]
    beta = bs[2]
  }
  return(c(alpha=alpha, beta=beta))
}
```
# Idea of the paper

@@

signatures <- read.csv("data/signatures.csv")
signatures %>% 
  ggplot(aes(x = x/1000)) + 
  geom_line(aes(y = raw_sig), colour = "grey70") +
  geom_line(aes(y = sig), colour = "grey30") +
  facet_grid(bullet~land) +
  ylim(c(-5,5)) +
  theme_bw() +
  ylab("Surface measurement (in microns)") +
  xlab("Relative Location (in millimeters)") 
```

@@

```{r, echo=FALSE, results = 'hide', warning = FALSE, message = FALSE}
features <- read.csv("data/fsi-features.csv.gz")
features <- features %>% mutate(
  bullet1 = gsub("ullet ","", bullet1),
  bullet2 = gsub("ullet ","", bullet2)
)
b12 <- features %>% filter(group1 == "G1", barrel1=="KA", bullet1== "B1",
                           group2 == "G1", barrel2=="KA", bullet2== "B2")
p1 <- b12 %>% ggplot(aes(x = land1, y = land2, fill = rfscore)) + 
  geom_tile() + ggtitle ("Same barrel") +  
  scale_fill_gradient2("RF score: ", midpoint=0.3, low = "darkgrey", high = "darkorange", limits=c(0,1)) +
  theme_bw() + 
  xlab ("Bullet 2") + ylab("Bullet 1") +
  theme(legend.position = "bottom") + coord_equal()

bab <- features %>% filter(group1 == "G1", barrel1=="KA", bullet1== "B1",
                           group2 == "G1", barrel2=="KB", bullet2== "B1")
p2 <- bab %>% ggplot(aes(x = land1, y = land2, fill = rfscore)) + 
  geom_tile() + ggtitle ("Different barrel") +  
  scale_fill_gradient2("RF score: ", midpoint=0.3, low = "darkgrey", high = "darkorange", limits=c(0,1)) +
  theme_bw() + 
  xlab ("Bullet 2") + ylab("Bullet 1") +
  theme(legend.position = "bottom") + coord_equal()
```

@@

```{r b2b, echo = FALSE, fig.width = 9, fig.height = 5,  out.width='.6\\textwidth', fig.cap="Overview of land-land matching scores for two pairs of bullet-bullet comparisons. On the left the two bullets are known to come from the same source (barrel) on the right, the bullets are from two different sources (barrels)"}
grid.arrange(p1, p2, ncol=2, padding=2)
```

@@

```{r sam-sketch, out.width='\\textwidth', fig.width=12, fig.height = 2.5, fig.cap="Sketch of all six land-to-land sequences between two bullets with six lands. "}
df2 <- data.frame(expand.grid(x = 1:6, y = 1:6))
df2$case1 <- df2$x == ((df2$y+5) %% 6) + 1
df2$case2 <- df2$x == ((df2$y+0) %% 6) + 1
df2$case3 <- df2$x == ((df2$y+1) %% 6) + 1
df2$case4 <- df2$x == ((df2$y+2) %% 6) + 1
df2$case5 <- df2$x == ((df2$y+3) %% 6) + 1
df2$case6 <- df2$x == ((df2$y+4) %% 6) + 1

df2 %>% gather("case", "values", starts_with("case")) %>% 
  mutate(case = gsub("case", "", case)) %>%
  mutate(case = paste0("k = ", as.numeric(case)-1)) %>%
  ggplot(aes(x = factor(x), y = factor(y, levels=1:6), fill = values)) + 
  geom_tile(colour = "grey20") + 
  facet_wrap(~case, ncol = 6) +
  xlab("Bullet 2") + ylab("Bullet 1") +
  scale_x_discrete(labels = paste0("L",1:6)) +
  scale_y_discrete(labels = paste0("L",1:6)) +
  scale_fill_manual("Cell included in SA(A,k)", values = c("white", "grey20")) + 
  coord_equal() +
  theme(legend.position="bottom")
```

@@

```{r h44, echo=FALSE, fig.width = 10, fig.height=5, fig.cap="Hamby set 44: overview of all bullet-to-bullet matches between all pairs of questioned bullets ($y$-axis) and known test fires from ten barrels ($x$ axis)."}
h44features <- read.csv("data/h44-features.csv")
# tank rash lands:
h44features <- h44features %>% mutate(
  rfscore = replace(rfscore, (bullet1 == "I" & land1 == 6) | (bullet2 == "I" & land2 == 6), NA)
)
h44features <- h44features %>% mutate(
  rfscore = replace(rfscore, (barrel1==8 & bullet1 == "1" & land1 == 6) | (barrel2==8 & bullet2 == "1" & land2 == 6), NA)
)

h44nest <- h44features %>% 
  filter(barrel1=="Unk") %>%
  filter(barrel1 != barrel2 | bullet1 != bullet2) %>%
  mutate(
    barrel1 = "Unknown",
    barrel2 = as.character(barrel2),
    barrel2 = replace(barrel2, barrel2=="Unk", "Unknown")
  ) %>%
  group_by(bullet1, barrel2, bullet2) %>%  nest()

h44nest <- h44nest %>%  mutate(
  sam_ccf = data %>% purrr::map_dbl(.f=function(d) {
    scores <- bulletxtrctr::compute_average_scores(d$land1, d$land2, d$ccf)
    max(scores)
  }),
  sam_rf = data %>% purrr::map_dbl(.f=function(d) {
    scores <- bulletxtrctr::compute_average_scores(d$land1, d$land2, d$rfscore)
    max(scores)
  })
  )
h44nest <- h44nest %>% 
  mutate(
    barrel2 = factor(barrel2, levels =c(1:10, "Unknown")),
    bullet1 = factor(bullet1, levels=rev(c("K", "O","L", "P",
                                           "J",
                                         "H", "I", "Y", "G",
                                         "E", "U", "X", "F", 
                                         "T", "S"))),
    bullet2 = factor(bullet2, levels=c(1:2, rev(levels(bullet1))))
  )
h44 <-  h44nest %>%
  ggplot(aes(y = bullet1, x = bullet2, 
             fill = sam_rf)) + 
  geom_tile(size=1) + 
  facet_grid(.~barrel2, space="free", scales = "free") +
  ylab("Questioned bullets") + 
  xlab("Testfires from barrels 1 to 10 (left), questioned bullets (right)") +
  scale_fill_gradient2("RF score ", low="darkgrey", 
                       high="darkorange", midpoint=0.35, limits=c(0,1)) + 
  scale_colour_manual("same source", values="darkorange") +

  #  scale_x_discrete(position = "top") +
  scale_y_discrete() +
  geom_tile(aes(colour = TRUE), size = .5, data = filter(h44nest, sam_rf > 0.3)) +
  guides(colour = guide_legend(override.aes = list(fill = NA))) + ggtitle("Hamby set 44") +
  theme_bw() +
    theme(legend.position="bottom")

@@

unknowns <- read.csv("data/pd-features-unknown.csv")
unknowns <- unknowns %>% filter(bullet1 != bullet2)
unknowns <- unknowns %>% mutate(
  bullet2 = gsub("Unknown 1-", "", bullet2),
  bullet1 = gsub("Unknown 1-", "", bullet1)
)
f3 <- rbind(
  f2 %>% select(b1, b2, barrel1, bullet1, 
                land1, bullet2, land2, ccf, rfscore, KM) %>%
    mutate(barrel2 = "Unknown"),
  unknowns %>% select(b1, b2, bullet1, 
                land1, bullet2, land2, ccf, rfscore) %>%
    mutate(barrel1 ="Unknown", barrel2="Unknown", KM=FALSE)
  )
pdnest <- f3 %>% group_by(bullet2, barrel1, bullet1) %>%  nest()

pdnest <- pdnest %>% mutate(
  sam_ccf = data %>% purrr::map_dbl(.f=function(d) {
    scores <- bulletxtrctr::compute_average_scores(d$land1, d$land2, d$ccf)
    max(scores)
  }),
  sam_rf = data %>% purrr::map_dbl(.f=function(d) {
    scores <- bulletxtrctr::compute_average_scores(d$land1, d$land2, d$rfscore)
    max(scores)
  }), 
  KM = data %>% purrr::map_lgl(.f=function(d) { any(d$KM) })
)

pdnest <- pdnest %>% 
  mutate(
    bullet2 = factor(bullet2, levels=rev(c("N", "B", "E", "T", "H", "J", "K", "Q", "Y", "Z"))),
    bullet1 = factor(bullet1, levels=c("B1", "B2", "B3", rev(levels(bullet2))))
  )
p3 <- pdnest %>%
  ggplot(aes(y = bullet2, x = bullet1, fill = sam_rf)) + 
  geom_tile(size=1) + 
  facet_grid(.~barrel1, scales="free", space="free") +
  ylab("Questioned bullets") + 
  xlab("Known bullets and Questioned bullets") +
  scale_fill_gradient2("RF score ", low="darkgrey", 
                       high="darkorange", midpoint=0.45, limits=c(0,1)) + 
  scale_colour_manual("same source", values="darkorange") + 
  scale_y_discrete() +
  theme_bw() +
  theme(legend.position="bottom") +
#  coord_equal() +
  geom_tile(aes(colour = TRUE), size = .5,
            data = filter(pdnest, KM)) +
  guides(colour = guide_legend(override.aes = list(fill = NA)))

@@

features <- features %>% mutate(
  bullet1 = gsub("ullet ","", bullet1),
  bullet2 = gsub("ullet ","", bullet2)
)

@@

hounest <- groups %>% mutate(
  sam_ccf = data %>% purrr::map_dbl(.f=function(d) {
    scores <- bulletxtrctr::compute_average_scores(d$land1, d$land2, d$ccf)
    max(scores)
  }),
  sam_rf = data %>% purrr::map_dbl(.f=function(d) {
    scores <- bulletxtrctr::compute_average_scores(d$land1, d$land2, d$rfscore)
    max(scores)
  })
)

@@

hou1nest <- hounest %>% filter(group1 == "G1") %>%
  mutate(
    bullet1 = factor(bullet1, levels=rev(c("U40", "U36", "U42", "U10", "U77", "U37", "U28", "U15"))),
    bullet2 = factor(bullet2, levels=c("B1", "B2", "B3", levels(bullet1)))
  )

hou1 <- hou1nest %>%
  ggplot(aes(y = bullet1, x = bullet2, fill = sam_rf)) + 
  geom_tile(size=1) + 
  facet_grid(.~barrel2, scales = "free", space="free") +
  ylab("Questioned bullets") + 
  xlab("Known bullets and Questioned bullets") +
  scale_fill_gradient2("RF score ", low="darkgrey", 
                       high="darkorange", midpoint=0.375, limits=c(0,1)) + 
  scale_y_discrete() +
  scale_colour_manual("same source", values="darkorange") +
  geom_tile(aes(colour = TRUE), size = .5, data = filter(hou1nest, sam_rf > 0.3)) +
  guides(colour = guide_legend(override.aes = list(fill = NA))) + ggtitle("Houston set 1")

hou2nest <- hounest %>% filter(group1 == "G2") %>%
  mutate(
    bullet1 = factor(bullet1, levels=rev(c("U23", "U41", "U61", "U98", "U73", "U34", "U63", "U66"))),
    bullet2 = factor(bullet2, levels=c("B1", "B2", "B3", levels(bullet1)))
  )
hou2 <-  hou2nest %>%
  ggplot(aes(y = bullet1, x = bullet2, fill = sam_rf)) + 
  geom_tile(size=1) + 
  facet_grid(.~barrel2, scales = "free", space="free") +
  ylab("Questioned bullets") + 
  xlab("Known bullets and Questioned bullets") +
  scale_fill_gradient2("RF score ", low="darkgrey", 
                       high="darkorange", midpoint=0.375, limits=c(0,1)) + 
  scale_y_discrete() +
    scale_colour_manual("same source", values="darkorange") +
  geom_tile(aes(colour = TRUE), size = .5, data = filter(hou2nest, sam_rf > 0.3)) +
  guides(colour = guide_legend(override.aes = list(fill = NA))) + ggtitle("Houston set 2")

hou3nest <- hounest %>% filter(group1 == "G3") %>%
  mutate(
    bullet1 = factor(bullet1, levels=rev(c("U27", "U33", "U36", "U49", "U56", "U65", "U14", "U45"))),
    bullet2 = factor(bullet2, levels=c("B1", "B2", "B3", levels(bullet1)))
  )

hou3 <- hou3nest %>%
  ggplot(aes(y = bullet1, x = bullet2, fill = sam_rf)) + 
  geom_tile(size=1) + 
  facet_grid(.~barrel2, scales = "free", space="free") +
  ylab("Questioned bullets") + 
  xlab("Known bullets and Questioned bullets") +
  scale_fill_gradient2("RF score ", low="darkgrey", 
                       high="darkorange", midpoint=0.375, limits=c(0,1)) + 
  scale_y_discrete() +
    scale_colour_manual("same source", values="darkorange") +
  geom_tile(aes(colour = TRUE), size = .5, data = filter(hou3nest, sam_rf > 0.3)) +
  guides(colour = guide_legend(override.aes = list(fill = NA))) + ggtitle("Houston set 3")

@@

```{r compare, fig.width = 8, fig.height = 5, fig.cap="Density curves of similarity scores from cross-correlation (top) and RF scores (bottom). Different colors indicate same source versus different source. Ideally all scores of different source pairs should be much lower than scores for same source pairs."}
nests <- rbind(
  h44nest %>% select(sam_rf, sam_ccf, samesource) %>%
    mutate(study = "Hamby-44", group1=NA),
  pdnest %>% select(sam_rf, sam_ccf, samesource) %>%
    mutate(study = "Phoenix PD", group1=NA),
  hounest %>% select(sam_rf, sam_ccf, samesource, group1) %>%
    mutate(study = "Houston FSI")
)
nests$study <- factor(nests$study, levels=c("Hamby-44", "Phoenix PD", "Houston FSI"))
nestslong <- nests %>% gather(key="measure", value="value", sam_rf, sam_ccf)
nestslong$measure <- factor(nestslong$measure)
levels(nestslong$measure) <- c("Cross-correlation", "RF score")

labels <- h44nest %>% filter( samesource, sam_rf < 0.5)
labels$comparison <- with(labels, paste(bullet1,"vs", paste(barrel2,bullet2,sep="-")))
labels$measure <- "RF score"
labels$study <- "Hamby-44"
labels$y <- 5+4:1
nestslong %>% ggplot(aes(x = value, fill=samesource, 
                     colour=samesource)) +
  geom_density(alpha=0.6) +
  geom_rug(alpha=0.5) +
  facet_grid(measure~study) +
  theme_bw() +
  scale_fill_manual("Same source", values=c("darkgrey", "darkorange")) +
  scale_colour_manual("Same source", values=c("darkgrey", "darkorange")) +
  scale_x_continuous("SAM scores", limits=c(0,1)) +
  theme(legend.position="bottom") +
  geom_hline(yintercept =0) +
  geom_text(aes(x = sam_rf, y = y, label=comparison), 
            hjust = 0,
            data = labels) +
  geom_segment(aes(x = sam_rf, xend = sam_rf, y = 0, yend = y), 
            size=0.1,
            colour="grey20",
            data = labels)

```

@@

\autoref{fig:tankrash} shows an overview of all lands of bullets in the Hamby-44 with major deficiencies, such as 'tank rash' or extreme pitting (holes caused by direct contact with burning gun powder).
```{r tankrash, fig.cap="Overview of bullet lands with prominent deficiency such as tank rash or extreme pitting in the Hamby-44 study.", fig.width=4, fig.height = 2, out.width='47.5%', fig.subcap=c("Br1-B1-L6", "Br2-B2-L5", "Br3-B1-L5", "Br8-B1-L6", "Br8-B2-L2", "Br8-B2-L6", "Unk-E-L6", "Unk-I-L6"), fig.align="middle", fig.ncol=2}
knitr::include_graphics(
  c('./images/B1-B1-L6.png', './images/B2-B2-L5.png',
    './images/B3-B1-L5.png', './images/B8-B1-L6.png',
    './images/B8-B2-L2.png', './images/B8-B2-L6.png',
    './images/NA-BE-L6.png', './images/NA-BI-L6.png')
)

```

>>>>

---
\newcommand{\hh}[1]{{\textcolor{orange}{#1}}}
\newcommand{\svp}[1]{{\textcolor{darkgreen}{#1}}}
\noindent

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  error = FALSE,
  collapse = TRUE,
  comment = "",
  fig.height = 6,
  fig.width = 6,
  fig.align = "center",
  out.width = "\\textwidth",
  cache = FALSE,
  fig.path = "figures/",
  echo = FALSE
)
options(knitr.table.format = "latex")

@@

```{r functions}
estimateBeta <- function(x, method = "mm", probs = c(0.25, 0.75)) {
  if (method == "mm") {
    mu <- mean(x, na.rm = TRUE)
    sd <- sd(x, na.rm = TRUE)
    lambda <- mu / sd * (1 - mu) / sd - 1
    alpha <- mu * lambda
    beta <- (1 - mu) * lambda
  }
  if (method == "LB") {
    quantile1 <- list(p = probs[1], x = quantile(probs = probs[1], x))
    quantile2 <- list(p = probs[2], x = quantile(probs = probs[2], x))
    bs <- LearnBayes::beta.select(quantile1, quantile2)
    alpha <- bs[1]
    beta <- bs[2]
  }
  return(c(alpha = alpha, beta = beta))
}
```
# Idea of the paper

@@

signatures <- read.csv("data/signatures.csv")
signatures %>%
  ggplot(aes(x = x / 1000)) +
  geom_line(aes(y = raw_sig), colour = "grey70") +
  geom_line(aes(y = sig), colour = "grey30") +
  facet_grid(bullet ~ land) +
  ylim(c(-5, 5)) +
  theme_bw() +
  ylab("Surface measurement (in microns)") +
  xlab("Relative Location (in millimeters)")
```

@@

```{r, echo=FALSE, results = 'hide', warning = FALSE, message = FALSE}
features <- read.csv("data/fsi-features.csv.gz")
features <- features %>% mutate(
  bullet1 = gsub("ullet ", "", bullet1),
  bullet2 = gsub("ullet ", "", bullet2)
)
b12 <- features %>% filter(
  group1 == "G1", barrel1 == "KA", bullet1 == "B1",
  group2 == "G1", barrel2 == "KA", bullet2 == "B2"
)
p1 <- b12 %>%
  ggplot(aes(x = land1, y = land2, fill = rfscore)) +
  geom_tile() + ggtitle("Same barrel") +
  scale_fill_gradient2("RF score: ", midpoint = 0.3, low = "darkgrey", high = "darkorange", limits = c(0, 1)) +
  theme_bw() +
  xlab("Bullet 2") + ylab("Bullet 1") +
  theme(legend.position = "bottom") + coord_equal()

bab <- features %>% filter(
  group1 == "G1", barrel1 == "KA", bullet1 == "B1",
  group2 == "G1", barrel2 == "KB", bullet2 == "B1"
)
p2 <- bab %>%
  ggplot(aes(x = land1, y = land2, fill = rfscore)) +
  geom_tile() + ggtitle("Different barrel") +
  scale_fill_gradient2("RF score: ", midpoint = 0.3, low = "darkgrey", high = "darkorange", limits = c(0, 1)) +
  theme_bw() +
  xlab("Bullet 2") + ylab("Bullet 1") +
  theme(legend.position = "bottom") + coord_equal()
```

@@

```{r b2b, echo = FALSE, fig.width = 9, fig.height = 5,  out.width='.6\\textwidth', fig.cap="Overview of land-land matching scores for two pairs of bullet-bullet comparisons. On the left the two bullets are known to come from the same source (barrel) on the right, the bullets are from two different sources (barrels)"}
grid.arrange(p1, p2, ncol = 2, padding = 2)
```

@@

```{r sam-sketch, out.width='\\textwidth', fig.width=12, fig.height = 2.5, fig.cap="Sketch of all six land-to-land sequences between two bullets with six lands. "}
df2 <- data.frame(expand.grid(x = 1:6, y = 1:6))
df2$case1 <- df2$x == ((df2$y + 5) %% 6) + 1
df2$case2 <- df2$x == ((df2$y + 0) %% 6) + 1
df2$case3 <- df2$x == ((df2$y + 1) %% 6) + 1
df2$case4 <- df2$x == ((df2$y + 2) %% 6) + 1
df2$case5 <- df2$x == ((df2$y + 3) %% 6) + 1
df2$case6 <- df2$x == ((df2$y + 4) %% 6) + 1

df2 %>%
  gather("case", "values", starts_with("case")) %>%
  mutate(case = gsub("case", "", case)) %>%
  mutate(case = paste0("k = ", as.numeric(case) - 1)) %>%
  ggplot(aes(x = factor(x), y = factor(y, levels = 1:6), fill = values)) +
  geom_tile(colour = "grey20") +
  facet_wrap(~case, ncol = 6) +
  xlab("Bullet 2") + ylab("Bullet 1") +
  scale_x_discrete(labels = paste0("L", 1:6)) +
  scale_y_discrete(labels = paste0("L", 1:6)) +
  scale_fill_manual("Cell included in SA(A,k)", values = c("white", "grey20")) +
  coord_equal() +
  theme(legend.position = "bottom")
```

@@

```{r h44, echo=FALSE, fig.width = 10, fig.height=5, fig.cap="Hamby set 44: overview of all bullet-to-bullet matches between all pairs of questioned bullets ($y$-axis) and known test fires from ten barrels ($x$ axis)."}
h44features <- read.csv("data/h44-features.csv")
# tank rash lands:
h44features <- h44features %>% mutate(
  rfscore = replace(rfscore, (bullet1 == "I" & land1 == 6) | (bullet2 == "I" & land2 == 6), NA)
)
h44features <- h44features %>% mutate(
  rfscore = replace(rfscore, (barrel1 == 8 & bullet1 == "1" & land1 == 6) | (barrel2 == 8 & bullet2 == "1" & land2 == 6), NA)
)

h44nest <- h44features %>%
  filter(barrel1 == "Unk") %>%
  filter(barrel1 != barrel2 | bullet1 != bullet2) %>%
  mutate(
    barrel1 = "Unknown",
    barrel2 = as.character(barrel2),
    barrel2 = replace(barrel2, barrel2 == "Unk", "Unknown")
  ) %>%
  group_by(bullet1, barrel2, bullet2) %>%
  nest()

h44nest <- h44nest %>% mutate(
  sam_ccf = data %>% purrr::map_dbl(.f = function(d) {
    scores <- bulletxtrctr::compute_average_scores(d$land1, d$land2, d$ccf)
    max(scores)
  }),
  sam_rf = data %>% purrr::map_dbl(.f = function(d) {
    scores <- bulletxtrctr::compute_average_scores(d$land1, d$land2, d$rfscore)
    max(scores)
  })
)
h44nest <- h44nest %>%
  mutate(
    barrel2 = factor(barrel2, levels = c(1:10, "Unknown")),
    bullet1 = factor(bullet1, levels = rev(c(
      "K", "O", "L", "P",
      "J",
      "H", "I", "Y", "G",
      "E", "U", "X", "F",
      "T", "S"
    ))),
    bullet2 = factor(bullet2, levels = c(1:2, rev(levels(bullet1))))
  )
h44 <- h44nest %>%
  ggplot(aes(
    y = bullet1, x = bullet2,
    fill = sam_rf
  )) +
  geom_tile(size = 1) +
  facet_grid(. ~ barrel2, space = "free", scales = "free") +
  ylab("Questioned bullets") +
  xlab("Testfires from barrels 1 to 10 (left), questioned bullets (right)") +
  scale_fill_gradient2("RF score ",
    low = "darkgrey",
    high = "darkorange", midpoint = 0.35, limits = c(0, 1)
  ) +
  scale_colour_manual("same source", values = "darkorange") +

  #  scale_x_discrete(position = "top") +
  scale_y_discrete() +
  geom_tile(aes(colour = TRUE), size = .5, data = filter(h44nest, sam_rf > 0.3)) +
  guides(colour = guide_legend(override.aes = list(fill = NA))) + ggtitle("Hamby set 44") +
  theme_bw() +
  theme(legend.position = "bottom")

@@

unknowns <- read.csv("data/pd-features-unknown.csv")
unknowns <- unknowns %>% filter(bullet1 != bullet2)
unknowns <- unknowns %>% mutate(
  bullet2 = gsub("Unknown 1-", "", bullet2),
  bullet1 = gsub("Unknown 1-", "", bullet1)
)
f3 <- rbind(
  f2 %>%
    select(
      b1, b2, barrel1, bullet1,
      land1, bullet2, land2, ccf, rfscore, KM
    ) %>%
    mutate(barrel2 = "Unknown"),
  unknowns %>%
    select(
      b1, b2, bullet1,
      land1, bullet2, land2, ccf, rfscore
    ) %>%
    mutate(barrel1 = "Unknown", barrel2 = "Unknown", KM = FALSE)
)
pdnest <- f3 %>% group_by(bullet2, barrel1, bullet1) %>% nest()

pdnest <- pdnest %>% mutate(
  sam_ccf = data %>% purrr::map_dbl(.f = function(d) {
    scores <- bulletxtrctr::compute_average_scores(d$land1, d$land2, d$ccf)
    max(scores)
  }),
  sam_rf = data %>% purrr::map_dbl(.f = function(d) {
    scores <- bulletxtrctr::compute_average_scores(d$land1, d$land2, d$rfscore)
    max(scores)
  }),
  KM = data %>% purrr::map_lgl(.f = function(d) {
    any(d$KM)
  })
)

pdnest <- pdnest %>%
  mutate(
    bullet2 = factor(bullet2, levels = rev(c("N", "B", "E", "T", "H", "J", "K", "Q", "Y", "Z"))),
    bullet1 = factor(bullet1, levels = c("B1", "B2", "B3", rev(levels(bullet2))))
  )
p3 <- pdnest %>%
  ggplot(aes(y = bullet2, x = bullet1, fill = sam_rf)) +
  geom_tile(size = 1) +
  facet_grid(. ~ barrel1, scales = "free", space = "free") +
  ylab("Questioned bullets") +
  xlab("Known bullets and Questioned bullets") +
  scale_fill_gradient2("RF score ",
    low = "darkgrey",
    high = "darkorange", midpoint = 0.45, limits = c(0, 1)
  ) +
  scale_colour_manual("same source", values = "darkorange") +
  scale_y_discrete() +
  theme_bw() +
  theme(legend.position = "bottom") +
  #  coord_equal() +
  geom_tile(aes(colour = TRUE),
    size = .5,
    data = filter(pdnest, KM)
  ) +
  guides(colour = guide_legend(override.aes = list(fill = NA)))

@@

features <- features %>% mutate(
  bullet1 = gsub("ullet ", "", bullet1),
  bullet2 = gsub("ullet ", "", bullet2)
)

@@

hounest <- groups %>% mutate(
  sam_ccf = data %>% purrr::map_dbl(.f = function(d) {
    scores <- bulletxtrctr::compute_average_scores(d$land1, d$land2, d$ccf)
    max(scores)
  }),
  sam_rf = data %>% purrr::map_dbl(.f = function(d) {
    scores <- bulletxtrctr::compute_average_scores(d$land1, d$land2, d$rfscore)
    max(scores)
  })
)

@@

hou1nest <- hounest %>%
  filter(group1 == "G1") %>%
  mutate(
    bullet1 = factor(bullet1, levels = rev(c("U40", "U36", "U42", "U10", "U77", "U37", "U28", "U15"))),
    bullet2 = factor(bullet2, levels = c("B1", "B2", "B3", levels(bullet1)))
  )

hou1 <- hou1nest %>%
  ggplot(aes(y = bullet1, x = bullet2, fill = sam_rf)) +
  geom_tile(size = 1) +
  facet_grid(. ~ barrel2, scales = "free", space = "free") +
  ylab("Questioned bullets") +
  xlab("Known bullets and Questioned bullets") +
  scale_fill_gradient2("RF score ",
    low = "darkgrey",
    high = "darkorange", midpoint = 0.375, limits = c(0, 1)
  ) +
  scale_y_discrete() +
  scale_colour_manual("same source", values = "darkorange") +
  geom_tile(aes(colour = TRUE), size = .5, data = filter(hou1nest, sam_rf > 0.3)) +
  guides(colour = guide_legend(override.aes = list(fill = NA))) + ggtitle("Houston set 1")

hou2nest <- hounest %>%
  filter(group1 == "G2") %>%
  mutate(
    bullet1 = factor(bullet1, levels = rev(c("U23", "U41", "U61", "U98", "U73", "U34", "U63", "U66"))),
    bullet2 = factor(bullet2, levels = c("B1", "B2", "B3", levels(bullet1)))
  )
hou2 <- hou2nest %>%
  ggplot(aes(y = bullet1, x = bullet2, fill = sam_rf)) +
  geom_tile(size = 1) +
  facet_grid(. ~ barrel2, scales = "free", space = "free") +
  ylab("Questioned bullets") +
  xlab("Known bullets and Questioned bullets") +
  scale_fill_gradient2("RF score ",
    low = "darkgrey",
    high = "darkorange", midpoint = 0.375, limits = c(0, 1)
  ) +
  scale_y_discrete() +
  scale_colour_manual("same source", values = "darkorange") +
  geom_tile(aes(colour = TRUE), size = .5, data = filter(hou2nest, sam_rf > 0.3)) +
  guides(colour = guide_legend(override.aes = list(fill = NA))) + ggtitle("Houston set 2")

hou3nest <- hounest %>%
  filter(group1 == "G3") %>%
  mutate(
    bullet1 = factor(bullet1, levels = rev(c("U27", "U33", "U36", "U49", "U56", "U65", "U14", "U45"))),
    bullet2 = factor(bullet2, levels = c("B1", "B2", "B3", levels(bullet1)))
  )

hou3 <- hou3nest %>%
  ggplot(aes(y = bullet1, x = bullet2, fill = sam_rf)) +
  geom_tile(size = 1) +
  facet_grid(. ~ barrel2, scales = "free", space = "free") +
  ylab("Questioned bullets") +
  xlab("Known bullets and Questioned bullets") +
  scale_fill_gradient2("RF score ",
    low = "darkgrey",
    high = "darkorange", midpoint = 0.375, limits = c(0, 1)
  ) +
  scale_y_discrete() +
  scale_colour_manual("same source", values = "darkorange") +
  geom_tile(aes(colour = TRUE), size = .5, data = filter(hou3nest, sam_rf > 0.3)) +
  guides(colour = guide_legend(override.aes = list(fill = NA))) + ggtitle("Houston set 3")

@@

```{r compare, fig.width = 8, fig.height = 5, fig.cap="Density curves of similarity scores from cross-correlation (top) and RF scores (bottom). Different colors indicate same source versus different source. Ideally all scores of different source pairs should be much lower than scores for same source pairs."}
nests <- rbind(
  h44nest %>%
    select(sam_rf, sam_ccf, samesource) %>%
    mutate(study = "Hamby-44", group1 = NA),
  pdnest %>%
    select(sam_rf, sam_ccf, samesource) %>%
    mutate(study = "Phoenix PD", group1 = NA),
  hounest %>%
    select(sam_rf, sam_ccf, samesource, group1) %>%
    mutate(study = "Houston FSI")
)
nests$study <- factor(nests$study, levels = c("Hamby-44", "Phoenix PD", "Houston FSI"))
nestslong <- nests %>% gather(key = "measure", value = "value", sam_rf, sam_ccf)
nestslong$measure <- factor(nestslong$measure)
levels(nestslong$measure) <- c("Cross-correlation", "RF score")

labels <- h44nest %>% filter(samesource, sam_rf < 0.5)
labels$comparison <- with(labels, paste(bullet1, "vs", paste(barrel2, bullet2, sep = "-")))
labels$measure <- "RF score"
labels$study <- "Hamby-44"
labels$y <- 5 + 4:1
nestslong %>%
  ggplot(aes(
    x = value, fill = samesource,
    colour = samesource
  )) +
  geom_density(alpha = 0.6) +
  geom_rug(alpha = 0.5) +
  facet_grid(measure ~ study) +
  theme_bw() +
  scale_fill_manual("Same source", values = c("darkgrey", "darkorange")) +
  scale_colour_manual("Same source", values = c("darkgrey", "darkorange")) +
  scale_x_continuous("SAM scores", limits = c(0, 1)) +
  theme(legend.position = "bottom") +
  geom_hline(yintercept = 0) +
  geom_text(aes(x = sam_rf, y = y, label = comparison),
    hjust = 0,
    data = labels
  ) +
  geom_segment(aes(x = sam_rf, xend = sam_rf, y = 0, yend = y),
    size = 0.1,
    colour = "grey20",
    data = labels
  )
```

@@

\autoref{fig:tankrash} shows an overview of all lands of bullets in the Hamby-44 with major deficiencies, such as 'tank rash' or extreme pitting (holes caused by direct contact with burning gun powder).
```{r tankrash, fig.cap="Overview of bullet lands with prominent deficiency such as tank rash or extreme pitting in the Hamby-44 study.", fig.width=4, fig.height = 2, out.width='47.5%', fig.subcap=c("Br1-B1-L6", "Br2-B2-L5", "Br3-B1-L5", "Br8-B1-L6", "Br8-B2-L2", "Br8-B2-L6", "Unk-E-L6", "Unk-I-L6"), fig.align="middle", fig.ncol=2}
knitr::include_graphics(
  c(
    "./images/B1-B1-L6.png", "./images/B2-B2-L5.png",
    "./images/B3-B1-L5.png", "./images/B8-B1-L6.png",
    "./images/B8-B2-L2.png", "./images/B8-B2-L6.png",
    "./images/NA-BE-L6.png", "./images/NA-BI-L6.png"
  )
)
```
